General discussion by Atom and Eva

In fact, until this point, the entire discussion section was a first-run, non-cherry picked composition by Eva.\footnote{link to youtube}

\section*{Broader Impact}

Authors are required to include a statement of the broader impact of their work, including its ethical aspects and future societal consequences. 
Authors should discuss both positive and negative outcomes, if any. For instance, authors should discuss a) 
who may benefit from this research, b) who may be put at disadvantage from this research, c) what are the consequences of failure of the system, and d) whether the task/method leverages
biases in the data. If authors believe this is not applicable to them, authors can simply state this.

Use unnumbered first level headings for this section, which should go at the end of the paper. {\bf Note that this section does not count towards the eight pages of content that are allowed.}

\subsection*{Future Work}

\begin{itemize}
\item This work was produced independalty from but converged to many of the same principles as Dr. Hinton's GLOM idea. Once made to work, \we plan to replace the \verb|PredNode|'s with \verb|GLOMNode|'s which are a much nicer formulation of the network of experts. GLOM has the added bonus of psuedo-STP training which is significantly more energy efficent and may be extremely quantized -- maybe even binarized -- during inference.
\item Atom and Eva are currently developing an massive multiagent online environment with on-demand \PGI agent interaction. More information will be posted at \texttt{https://limboid.ai}.
\item Autonomously develop and train robots with embodied \PGI.
\end{itemize}


\begin{ack}
\We thank Dr. Linda S. Barasch from the University of Texas at Arlington for assisting in publishing this paper. \We also thank all \our references and the entire research community for their contributions. 

This work is a completely independant study. It has no financial incentives and is personally financed.
\end{ack} 
