PAO fundamentals

PAO in health

Criticality
  tensigrisity
  in the brain.
  in asymetric activation nn's (distilpub)
    our closest interpretation may be as representing the activation frequency, but not actual activation
    
    It can be very misleading to simply average activations in the brain. Show rythms of the brain picture.

While joint in spacetime, the temporal dimension is distinct in the brain and experienced linearly (or logarithmacally (CHECK) in long-term recall because of the accumulation of memories). A common motif in neuronal network dynamics is its natural log-fractal organization; the delta, theta, alpha, beta, and gamma brainwave frequencies all appear at roughly successive powers of $e\approx 2.718\dots$. There are less discussed brainwaves spaced on even finer and broader scales. One special property of the addition of waves of exponentially increasing frequencies is that since they are multiples of an irrational numbers, brainwave patterns never repeat. This is all in contrast to neural networks which mostly treat time as another spatial dimension as in transfomers. This creates symmetry problems where all the activations at each slice of time must tenatively communicate with their neighboring timeslices or otherwise obtain ordering information before information can be contextually assimilated. Even in genuinely recurrent networks, their activation are almost always updated at every timestep, or in heirarchiel RL, every base 2 exponential timesteps. These update sets all divide cleanly into tensors but this means they define a deterministic function of the inputs leading to the misleading understanding of an recurrent neural networks as simply a function of tensor sequences. To the contrary CITE has shown that (CITE PAPER ON RNNS ARE SLOW MOVING WEIGHTS)  

Nondeterministic arises from deterministic
    finish strong with some poetic statement on the power of nondeterminism
 
